Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-07-14 article-models-ttinternal.tex
progress on substitution algebras

\begin{rmk}
In this remark we explain what it means that weakening is a pre-weakening
homomorphism. Let $\cftalg{A}$ be a pre-weakening algebra. Then its weakening
$\cftwk{\cftalg{A}}$ is a CFT-homomorphism from
$\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}$ to
$\cftfamalg{\cftfamalg{\cftalg{A}}}$. Therefore, $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism if the diagram
\begin{equation*}
\begin{tikzcd}[column sep=8em]
\ctxwk
  {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}
    { \ctxwk
        {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
        {\cftfamhom{\cftwk{\cftalg{A}}}}
      }
  \ar{d}[swap]{\cftwk{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
    {\cftwkc{\cftalg{A}}}
    {\ctxwk{\cftalgf{\cftalg{B}}}{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
  \ar{d}
    { \jcomp{}
        { \cftwkf{\cftalg{A}}}
        { \jcomp{}
            { \cftwkc{\cftalg{A}}}
            { \cftwk{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
      }
  \\
\cftfamalg{\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}[swap]
    { \cftfamhom
        { \cftfamhom
            { \cftwk{\cftalg{A}}}
          }
      }
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
      {\cftwkc{\cftalg{A}}}
      {\cftfamalg{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
\end{tikzcd}
\end{equation*}
Both the domain and the codomain are
again pre-weakening algebras: the weakening of
$\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}$ is
$\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamhom{\cftwk{\cftalg{A}}}}$; the weakening of
$\cftfamalg{\cftfamalg{\cftalg{A}}}$ is
$\cftfamhom{\cftfamhom{\cftwk{\cftalg{A}}}}$. Therefore, the condition that
the weakening of $\cftalg{A}$ is a pre-weakening homomorphism becomes that
the diagram
\end{rmk}

\subsubsection{Currying for weakening}
Let $\cftalg{A}$ be a CFT-algebra in context $\Gamma$ and let
\begin{equation*}
\jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
  {\cftfamalg{\cftfamalg{\cftalg{A}}}}
  {\cftwk{\cftalg{A}}}
\end{equation*}
be a CFT-homomorphism. The abstraction of the rules in \autoref{comp-ew} is the
condition that the diagram
\begin{equation}\label{diag:cftwk-cftextcurry}
\begin{tikzcd}[column sep=large]
\ctxwk
  {\ctxext{\cftalgf{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\cftalg{A}}}
  \ar{r}{\ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftwk{\cftalg{A}}}}
  \ar{dr}[swap]{\jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}}
& \ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{d}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
  \\
& \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}
\end{tikzcd}
\end{equation}
of CFT-algebras in context 
$\ctxext
    {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
    {\cftalgf{\cftfamalg{\cftalg{A}}}}
$ %
commutes.

@@

\subsubsection{Weakening by the empty family}
\begin{equation}\label{eq:cftwk-cftempcurry}
\jhomeq
  { {\Gamma}{\cftalgc{\cftalg{A}}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \subst{\cftempf{\cftalg{A}}}{\cftwk{\cftalg{A}}}
    }
  { id_{\cftfamalg{\cftalg{A}}}
    }
\end{equation}

@@

\begin{proof}
All one has to do to prove this is to substitute all of the ingredients of
the diagram in \autoref{diag:cftwk-cftwk} consecutively by
$\gamma$, by $a$, by $b$ and finally by $q$.
\end{proof}

@@

\begin{defn}
A weakening algebra in context $\Gamma$ is a CFT-algebra $\cftalg{A}$ in context
$\Gamma$ for which there is a CFT-homomorphism
\begin{equation*}
\jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
  {\cftalg{F_{F_A}}}
  {\cftwk{\cftalg{A}}}
\end{equation*}
satisfying the judgmental equalities of %
\autoref{diag:cftwk-cftwk,diag:cftwk-cftextcurry,eq:cftwk-cftempcurry}.
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Substitution algebras}
Substitution algebras will be CFT-algebras with an additional substitution 
operation. Given a CFT-algebra $\cftalg{A}$ in context $\Gamma$, substitution 
will be a CFT-homomorphism
\begin{equation*}
\jhom
  {{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}
  {\cftfamalg{\cftalg{A}}}
  {\cftsubst{\cftalg{A}}}
\end{equation*}
We will require additionally that substitution preserves itself. Thus, we will
formulate an abstraction of the rules stated in \autoref{comp-ss}.

\begin{defn}
Let $\cftalg{A}$ be a CFT-algebra in context $\Gamma$ and let
\begin{equation*}
\jhom
  {{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}
  {\cftfamalg{\cftalg{A}}}
  {\cftsubst{\cftalg{A}}}
\end{equation*}
be a CFT-homomorphism. We say that the pair $(\cftalg{A},\cftsubst{\cftalg{A}})$
is a substitution algebra in context $\Gamma$ if the diagram
\begin{equation}\label{diag:cftsubst-cftsubst}
\begin{tikzcd}[column sep=9em]
\ctxwk
  { \cftalgt{\cftalg{A}}}
  { { \cftalgt{\cftfamalg{\cftfamalg{\cftalg{A}}}}}
    { \cftfamalg{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
  \ar{r}
    { \ctxwk
        { \cftalgt{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
                { \cftctxext}
                { \cftsubst{\cftalg{A}}}
              }
          }
      }
  \ar{d}[swap]
    { \ctxwk
        { { \cftalgt{\cftalg{A}}}
          { \cftalgt{\cftfamalg{\cftfamalg{\cftalg{A}}}}}
          }
        { \jcomp{}{\ctxwk{\cftalgt{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftfamext}}}{\cftfamhom{\cftsubst{\cftalg{A}}}}}
      }
  & 
\ctxwk
  { \cftalgt{\cftalg{A}}}
  { \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}
  \ar{d}{ \cftfamhom{\cftsubst{\cftalg{A}}}}
  \\
\ctxwk
  { { \cftalgt{\cftalg{A}}}
    { \cftalgt{\cftfamalg{\cftfamalg{\cftalg{A}}}}}
    }
  { \jcomp{}
      { \ctxwk{\cftalgt{\cftalg{A}}}{\jcomp{}{\cftctxext}{\cftfamext}}}
      { \jcomp{}
          {\cftsubstc{\cftalg{A}}}
          {\cftfamalg{\cftfamalg{\cftalg{A}}}}
        }
    }
  \ar{r}
& \jcomp{}{\cftsubstc{\cftalg{A}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
\end{tikzcd}
\end{equation}
of CFT-algebras in context 
$ \ctxext
    { { { { { {\Gamma}
              {\cftalgc{\cftalg{A}}}
              }
            { \cftalgf{\cftalg{A}}}
            }
          { \cftalgt{\cftalg{A}}}
          }
        { \ctxwk{\cftalgt{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}}
        }
      { \ctxwk{\cftalgt{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
      }
    { \ctxwk{\cftalgt{\cftalg{A}}}{\cftalgt{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}$
commutes judgmentally.
\end{defn}

\begin{rmk}
We shall have to verify that the diagram in \autoref{diag:cftsubst-cftsubst} is
well-typed.
\end{rmk}

>>>>

\begin{rmk}\label{rmk:cftwk-prewk}
In this remark we explain what it means that weakening is a pre-weakening
homomorphism. Let $\cftalg{A}$ be a pre-weakening algebra. Then its weakening
$\cftwk{\cftalg{A}}$ is a CFT-homomorphism from
$\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}$ to
$\cftfamalg{\cftfamalg{\cftalg{A}}}$. Therefore, $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism if the diagram
\begin{equation*}
\begin{tikzcd}[column sep=8em]
\ctxwk
  {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}
    { \ctxwk
        {\cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
        {\cftfamhom{\cftwk{\cftalg{A}}}}
      }
  \ar{d}[swap]{\cftwk{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
    {\cftwkc{\cftalg{A}}}
    {\ctxwk{\cftalgf{\cftfamalg{\cftfamalg{\cftalg{A}}}}}{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
  \ar{d}
    { \jcomp{}
        { \cftwkf{\cftalg{A}}}
        { \jcomp{}
            { \cftwkc{\cftalg{A}}}
            { \cftwk{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
      }
  \\
\cftfamalg{\cftfamalg{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  \ar{r}[swap]
    { \cftfamhom
        { \cftfamhom
            { \cftwk{\cftalg{A}}}
          }
      }
  &
\jcomp{}
  { \cftwkf{\cftalg{A}}}
  { \jcomp{}
      {\cftwkc{\cftalg{A}}}
      {\cftfamalg{\cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}}}
    }
\end{tikzcd}
\end{equation*}
of pre-weakening algebras in context
$ \ctxext
    { { { { \Gamma}
          { \cftalgc{\cftalg{A}}}
          }
        { \cftalgf{\cftalg{A}}}
        }
      { \ctxwk{\cftalgf{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
      }
    { \cftalgf{\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
      }$
commutes judgmentally.
\end{rmk}

\begin{comment}
\subsubsection{Currying for weakening}
Let $\cftalg{A}$ be a CFT-algebra in context $\Gamma$ and let
\begin{equation*}
\jhom
  {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
  {\ctxwk{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
  {\cftfamalg{\cftfamalg{\cftalg{A}}}}
  {\cftwk{\cftalg{A}}}
\end{equation*}
be a CFT-homomorphism. The abstraction of the rules in \autoref{comp-ew} is the
condition that the diagram
\begin{equation}\label{diag:cftwk-cftextcurry}
\begin{tikzcd}[column sep=large]
\ctxwk
  {\ctxext{\cftalgf{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\cftalg{A}}}
  \ar{r}{\ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftwk{\cftalg{A}}}}
  \ar{dr}[swap]{\jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}}
& \ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{d}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
  \\
& \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}
\end{tikzcd}
\end{equation}
of CFT-algebras in context 
$\ctxext
    {{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}
    {\cftalgf{\cftfamalg{\cftalg{A}}}}
$ %
commutes.

@@

\subsubsection{Weakening by the empty family}
\begin{equation}\label{eq:cftwk-cftempcurry}
\jhomeq
  { {\Gamma}{\cftalgc{\cftalg{A}}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \subst{\cftempf{\cftalg{A}}}{\cftwk{\cftalg{A}}}
    }
  { \cftidhom{\cftfamalg{\cftalg{A}}}
    }
\end{equation}

@@

\begin{proof}
All one has to do to prove this is to substitute all of the ingredients of
the diagram in \autoref{diag:cftwk-cftwk} consecutively by
$\gamma$, by $a$, by $b$ and finally by $q$.
\end{proof}
\end{comment}

@@

\begin{defn}
A weakening algebra in context $\Gamma$ is a pre-weakening algebra $\cftalg{A}$
in context $\Gamma$ for which the weakening $\cftwk{\cftalg{A}}$ is a
pre-weakening homomorphism as explained in \autoref{rmk:cftwk-prewk},
satisfying the two additional judgmental equalities
expressing that: (1) the diagram
\begin{equation}\label{diag:cftwk-cftextcurry}
\begin{tikzcd}[column sep=large]
\ctxwk
  {\ctxext{\cftalgf{\cftalg{A}}}{\cftalgf{\cftfamalg{\cftalg{A}}}}}
  {\cftfamalg{\cftalg{A}}}
  \ar{r}{\ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftwk{\cftalg{A}}}}
  \ar{dr}[swap]{\jcomp{}{\cftfamext}{\cftwk{\cftalg{A}}}}
& \ctxwk{\cftalgf{\cftfamalg{\cftalg{A}}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{d}{\jcomp{}{\cftctxext}{\cftwk{\cftalg{A}}}}
  \\
& \cftfamalg{\cftfamalg{\cftfamalg{\cftalg{A}}}}
\end{tikzcd}
\end{equation}
and (2) that
\begin{equation}\label{eq:cftwk-cftempcurry}
\jhomeq
  { {\Gamma}{\cftalgc{\cftalg{A}}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \cftfamalg{\cftalg{A}}
    }
  { \subst{\cftempf{\cftalg{A}}}{\cftwk{\cftalg{A}}}
    }
  { \cftidhom{\cftfamalg{\cftalg{A}}}
    }
\end{equation}
\end{defn}

\begin{rmk}
The condition in \autoref{diag:cftwk-cftextcurry} implements the rules of
\autoref{comp-ew} and the condition in \autoref{eq:cftwk-cftempcurry} implements
the rules of \autoref{comp-0w}.
\end{rmk}

\begin{defn}
A \emph{weakening homomorphism} is a pre-weakening homomorphism between
weakening algebras.
\end{defn}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Substitution algebras}
\begin{defn}
A \emph{pre-substitution algebra $\cftalg{A}$ in context $\Gamma$} consists of a
CFT-algebra $\cftalg{A}$ in context $\Gamma$ and a CFT-homomorphism
\begin{equation*}
\jhom
  {{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}
  {\ctxwk{\cftalgt{\cftalg{A}}}{{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}}
  {\cftsubst{\cftalg{A}}}.
\end{equation*}
\end{defn}

\begin{defn}
Suppose $\cftalg{A}$ is a pre-substitution algebra in context $\Gamma$. Then we
define the pre-substitution algebra $\cftfamalg{\cftalg{A}}$ in context 
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$ by taking
\begin{equation*}
\cftsubst{\cftfamalg{\cftalg{A}}}
  \defeq \jcomp{}{\cftctxext}{\cftsubst{\cftalg{A}}}.
\end{equation*}
\end{defn}

\begin{defn}
Suppose $\cftalg{Q}$ is a pre-substitution algebra in context $\ctxext{\Gamma}{B}$ and
let $\jfam{\Gamma}{A}$. Then we define the pre-substitution algebra 
$\ctxwk{A}{\cftalg{Q}}$ in context $\ctxext{{\Gamma}{A}}{\ctxwk{A}{B}}$ by 
taking
\begin{equation*}
\cftsubst{\ctxwk{A}{\cftalg{Q}}}\defeq \ctxwk{A}\cftsubst{\cftalg{Q}}.
\end{equation*}
\end{defn}

\begin{defn}
Suppose $\cftalg{Q}$ is a pre-substitution algebra in context $\ctxext{{\Gamma}{A}}{P}$
and let $\jterm{\Gamma}{A}{x}$. Then we define the pre-substitution algebra 
$\subst{x}{\cftalg{Q}}$ in context $\ctxext{\Gamma}{\subst{x}{P}}$ by taking
\begin{equation*}
\cftsubst{\subst{x}{\cftalg{Q}}} \defeq \subst{x}{\cftsubst{\cftalg{Q}}}.
\end{equation*}
\end{defn}

\begin{defn}
A \emph{pre-substitution homomorphism $\cfthom{f}$ from $\cftalg{A}$ to $\cftalg{B}$ in
context $\Gamma$} is a CFT-homomorphism $\cfthom{f}$ for which the diagram
\begin{equation*}
\begin{tikzcd}[column sep=8em]
\ctxwk{\cftalgt{\cftalg{A}}}{\cftfamalg{\cftfamalg{\cftalg{A}}}}
  \ar{r}{\ctxwk{\cftalgt{\cftalg{A}}}{\cftfamhom{\cftfamhom{\cfthom{f}}}}}
  \ar{d}[swap]{\cftsubst{\cftalg{A}}}
  &
\jcomp{}
  { \cfthomt{\cfthom{f}}}
  { \jcomp{}
      { \cfthomf{\cfthom{f}}}
      { \jcomp{}
          { \cfthomc{\cfthom{f}}}
          { \ctxwk{\cftalgt{\cftalg{B}}}{\cftfamalg{\cftfamalg{\cftalg{B}}}}}
        }
    }
  \ar{d}
    { \jcomp{}
        { \cfthomt{\cfthom{f}}}
        { \jcomp{}
            { \cfthomf{\cfthom{f}}}
            { \jcomp{}
                { \cfthomc{\cfthom{f}}}
                {\cftsubst{\cftalg{B}}}
              }
          }
      }   
  \\
\ctxwk{\cftalgt{\cftalg{A}}}{{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
  \ar{r}[swap]
    {\ctxwk{\cftalgt{\cftalg{A}}}{{\cftalgf{\cftalg{A}}}{\cftfamhom{\cfthom{f}}}}}
  &
\jcomp{}
  { \cfthomt{\cfthom{f}}}
  { \jcomp{}
      { \cfthomf{\cfthom{f}}}
      { \jcomp{}
          { \cfthomc{\cfthom{f}}}
          { \ctxwk
              {\cftalgt{\cftalg{B}}}
              {{\cftalgf{\cftalg{B}}}{\cftfamalg{\cftalg{B}}}}
            }
        }
    }
\end{tikzcd}
\end{equation*}
of pre-substitution algebras in context
$\ctxext{{{\Gamma}{\cftalgc{\cftalg{A}}}}{\cftalgf{\cftalg{A}}}}{\cftalgt{\cftalg{A}}}$
commutes judgmentally.
\end{defn}

\begin{defn}
A \emph{substitution algebra in context $\Gamma$} is a pre-substitution algebra
in context $\Gamma$ for which substitution is a pre-substitution homomorphism.
\end{defn}

\begin{rmk}
The condition that the substitution of a pre-substitution algebra is a
pre-substitution homomorphism assert that the diagram
\begin{small}
\begin{equation*}
\begin{tikzcd}[column sep=large]
\ctxwk
  {\cftalgt{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
  {\cftfamalg{\cftfamalg{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}}
  \ar{r}
    { \ctxwk
        {\cftalgt{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
        {\cftfamhom{\cftfamhom{\cftsubst{\cftalg{A}}}}}
      }
  \ar{d}[swap]
    {\cftsubst{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
  &
\jcomp{}
  { \cftsubstt{\cftalg{A}}}
  { \jcomp{}
      { \cftsubstf{\cftalg{A}}}
      { \jcomp{}
          { \cftsubstc{\cftalg{A}}}
          { \ctxwk
              { \cftalgt
                  { \ctxwk
                      { \cftalgt{\cftalg{A}}}
                      { {\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
                    }
                }
              { \cftfamalg
                  { \cftfamalg
                      { \ctxwk
                          { \cftalgt{\cftalg{A}}}
                          { {\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
                        }
                    }
                }
            }
        }
    }
  \ar{d}
    { \jcomp{}
        { \cftsubstt{\cftalg{A}}}
        { \jcomp{}
            { \cftsubstf{\cftalg{A}}}
            { \jcomp{}
                { \cftsubstc{\cftalg{A}}}
                { \cftsubst
                    { \ctxwk
                        {\cftalgt{\cftalg{A}}}
                        {{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
                      }
                  }
              }
          }
      }
  \\
\ctxwk
  { \cftalgt{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
  { {\cftalgf{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
    {\cftfamalg{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
    }
  \ar{r}[swap,yshift=-1em]
    { \ctxwk
        { \cftalgt{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
        { {\cftalgf{\ctxwk{\cftalgt{\cftalg{A}}}{\cftalg{F_{F_A}}}}}
          {\cftfamhom{\cftsubst{\cftalg{A}}}}}
          }
  &
\jcomp{}
  { \cftsubstt{\cftalg{A}}}
  { \jcomp{}
      { \cftsubstf{\cftalg{A}}}
      { \jcomp{}
          { \cftsubstc{\cftalg{A}}}
          { \ctxwk
              { \cftalgt
                  { \ctxwk
                      {\cftalgt{\cftalg{A}}}
                      {{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
                    }
                }
              { { \cftalgf
                    { \ctxwk
                        { \cftalgt{\cftalg{A}}}
                        {{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
                      }
                  }
                { \cftfamalg
                    { \ctxwk
                        {\cftalgt{\cftalg{A}}}
                        {{\cftalgf{\cftalg{A}}}{\cftfamalg{\cftalg{A}}}}
                      }
                  }
                }
            }
        }
    }
\end{tikzcd}
\end{equation*}
\end{small}
\end{rmk}

\begin{defn}
A substitution homomorphism is a pre-substitution homomorphism between
substitution algebras.
\end{defn}
